DeepSphere: a graph-based spherical CNN

### 2019-09-19 main.tex
Updates from Overleaf

\paragraph{Theoretical convergence.}
We extend the work Belkin and Nyiogi to a fixed sampling. 
Given a sampling $V = \{x_0, \dots, x_{n-1}\}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
\begin{theorem}
	For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} \b{L}_n^{t_n} T_{V_n} f(y) =  \Delta_{\mathbb{S}^2}f(y).$$
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
While this is \emph{not} a proof of equivariance of the graph convolution for a specific sampling, we observe that the $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation. 
To have the desired equality in eq..., we would need to prove a stronger result, for example uniform convergence (in the space of the operators).
\nati{Should we put this here?: }
This does not hold in general \cite{belkin2007convergence}. However, we believe that this is achievable for a bandlimited signals.
More importantly, the proof of theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix ... inspires us in the construction of our graph Laplacian. a) use gaussian kernel b) we need to adjust t with respect of n such that ...
\nati{While do not have a proof for it, we srongly believe that the HEALpix sampling do satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}. This is discussed in Appendix~\ref{...}}

% 3) Show experimental results
\paragraph{Empirical convergence.}
\nati{@martino, please put some stuff here...}
Explain the difference of errors... Uniform sampling is better

>>>>

\paragraph{Theoretical convergence.}
We extend the work Belkin and Nyiogi to a fixed sampling. 
Given a sampling $V = \{x_0, \dots, x_{n-1}\}$ define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, define $A_i$ to be its corresponding area and $d_i$ to be the radius of the smallest ball in $\mathbb R^3$ containing $\sigma_i$. Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
\begin{theorem}
	For a sampling $\mathcal P = \{x_i\in\mathbb S^2\}_{i=0}^{n-1}$ of the sphere that is equi area and such that $d^{(n)} \leq \frac{C}{\sqrt{n}}$, for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the euclidean distance in $\mathbb R^3$, for all $y\in\mathbb S^2$, there exists a sequence $t_n = n^\beta$ such that the rescaled Heat Kernel Graph Laplacian operator $\frac{|\mathbb S^2|}{4\pi t_n}L^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\triangle_{\mathbb S^2}$  for $n\to\infty$:
	$$ \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n} \b{L}_n^{t_n} T_{V_n} f(y) =  \Delta_{\mathbb{S}^2}f(y).$$
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
This theorem show that the $\b{L}$ converges pointwisely toward an operator ($\Delta_{\mathbb S^2}$) commuting with rotation and hence is a strong hints for equivariance.
Importantly, the proof of Theorem \ref{theo:pointwise convergence for a regular sampling} in Appendix \ref{...} inspires us in the construction of our graph Laplacian. It gives us a strong hint how the parameter $t$ needs to adjusted with respect of the number of point $n$.

It is important to keep in mind the limits of Theorem \ref{theo:pointwise convergence for a regular sampling}.
First, it is \emph{not} a proof of equivariance of the graph convolution for a specific sampling. To construct such a proof, a stronger convergence result is needed, for example uniform convergence (instead of pointwise).
Unfortunately, the graph laplacian does \emph{not} converges uniformly in general \cite{belkin2007convergence}. This can probably be overcomed by considering a specific class of functions, such as bandlimited function.
Second, while do not have a proof for it, we strongly believe that the HEALpix sampling do satisfy the hypothesis $d^{(n)}\leq \frac{C}{\sqrt{n}}$ of Theorem \ref{theo:pointwise convergence for a regular sampling}. This is discussed in Appendix~\ref{...}

% 3) Show experimental results
\paragraph{Empirical convergence.}
From 20\% error on V1, we got to less than 2\% error on v2. More neighbors, more precision, plus a better kernel width obtained "minimizing" the equivariance error. How to explain how we found the kernel width? Because minimizing the kernel width would lead to a completely disconnected graph. What we did was finding a heuristic law (fix neighbors, set the kernel width by imposing the minimum weight to be equal to $0.1$) and then optimizing
\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{DeepSphereV1}
	\caption{Shall we put it here or in Appendix?
	}
	\label{fig:deepsphereV1}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{DeepSphereV2_50neighbors.pdf}
	\caption{}
	\label{fig:deepsphereV2}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{khasanova_frossard.pdf}
	\caption{}
	\label{fig:khasanova_frossard}
\end{figure}
Explain the difference of errors... Uniform sampling is better
